Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-23 02_methods/methods.tex
Update the normalization roughly

Before to standardize each sequence, the first step of the normalization is to cancel the intensity shift which is specific for each patient.
The intensity \ac{pdf} do not follow either a Rician or Gaussian distribution over time.
Therefore, the mean cannot be used as a potential estimate for the offset.
Additionally, this offset should be characterized by a smooth transition over time.
This problem can be solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{fig:heatmap}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar of the heatmap as a node and connecting each pair of bars by an edge.
The edge weight $w_{ij}$ between two nodes $i$ and $j$ corresponding to two pixels at position $(x_i, y_i)$ and $(x_j, y_j)$, respectively, is defined as in Eq.\,\eqref{eq:weight}:

\begin{equation}
  w_{ij} = \begin{cases}
    \alpha \exp(1 - \frac{H(i)}{\max(H)})       & \text{if } x_j = x_i + 1 \text{ and } y_j = y_i \\
    (1 - \alpha) \exp(1 - \frac{H(i)}{\max(H)}) & \text{if } x_j = x_i \text{ and } y_j = y_i + 1 \\
    0                                           & \text{otherwise}
  \end{cases} ,
  \label{eq:weight}
\end{equation}

@@

Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra algorithm.
The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
To ensure a robust estimation of the offset, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
The procedure is stopped once that the offset found do not change.
In general, this process is not repeated more than 3 iterations.
An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
Finally, each sequence is shifted using this offset.

@@

The next variations to correct are the time offset and the data dispersion.
By computing the \ac{rmse} for each \ac{dce}-\ac{mri}, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
The parametric model to perform the registration is formulated as in Eq.\,\eqref{eq:model}:

@@

Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
Once all these parameters have been inferred, the data can be shifted as well as scale.

>>>>

Before to standardize each sequence, the first step of the normalization is to cancel the intensity specific at each patient, occurring due to the media injection.
In \ac{dce}-\ac{mri}, the intensity \ac{pdf} do not always follow either a Rician or a Gaussian distribution over time.
Therefore, the mean of these distributions cannot be used as a potential estimate for this offset.
Additionally, this offset should be characterized by a smooth transition between series over time.
Thus, this problem is solved using the graph-theory: considering the intensity \ac{pdf} over time as shown in Fig.\,\ref{fig:heatmap}, the offset is the boundary splitting the heatmap in two partitions such that it is as close as possible to the peak of the intensity \ac{pdf} (see Fig.\,\ref{fig:estimator} for an illustration).
Given the heatmap, a directed weighted graph $\mathcal{G}=(\mathcal{V}, \mathcal{E})$ is built by taking each bar of the heatmap as a node and connecting each pair of bars by an edge.
The edge weight $w_{ij}$ between two nodes $i$ and $j$ corresponding to two pixels at position $(x_i, y_i)$ and $(x_j, y_j)$, respectively, is defined as in Eq.\,\eqref{eq:weight}:

\begin{equation}
  w_{ij} = \begin{cases}
    \alpha \exp(1 - \frac{H(i)}{\max(H)})       & \text{if } x_j = x_i + 1 \text{ and } y_j = y_i, \\
    (1 - \alpha) \exp(1 - \frac{H(i)}{\max(H)}) & \text{if } x_j = x_i \text{ and } y_j = y_i + 1, \\
    0                                           & \text{otherwise},
  \end{cases}
  \label{eq:weight}
\end{equation}

@@

Therefore, the offset is estimated by finding the shortest-path to cross the graph using Dijkstra's algorithm.
The entry and exiting nodes are set to be the bin with the maximum probability for the first \ac{dce}-\ac{mri} serie and the bin corresponding to the median value for the last \ac{dce}-\ac{mri} serie, respectively.
To ensure a robust estimation of the offset, the process of finding the shortest-path is iteratively repeated by shifting the data and updating the heatmap as well as the graph $\mathcal{G}$.
The procedure is stopped once that the offset found do not change.
In general, this process is not repeated more than 3 iterations.
An example of the offset found using this approach is presented in Fig.\,\ref{fig:estimator}.
Finally, for each \ac{dce}-\ac{mri} serie, the intensities are shifted by this offset.

@@

The next variations to correct are the time offset and the data dispersion.
By computing the \ac{rmse} of the intensities for each \ac{dce}-\ac{mri} serie, one can observed these two variations as shown in Fig.\,\ref{fig:rmse}.
Therefore, to correct these variations, we propose to register each patient \ac{rmse} to a mean model which corresponds to the mean of all patients \ac{rmse}.
The parametric model to perform the registration is formulated as in Eq.\,\eqref{eq:model}:

@@

Illustration of the correction applied to each \ac{rmse} patient is shown in Fig.\,\ref{fig:rmseal}.
Once all these parameters have been inferred, the data can be shifted as well as scaled.
